hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2024-12-06 inst/manuscript/paper.Rmd
mess around with format ouput (e.g. JOSS)

```{r}
plot_check_temp(data = year_sim,
                dates = date,
                temperature = temp,
                temp_min = 0, # temp_min and max lines are user customizable
                temp_max = 25)
```

There are no obvious outliers but since each day has 48 records, we need to summarize it to daily mean temperature with `summarize_temp()` and then check for missing days with `check_continuous()`. We also recommend using `plot_check_temp()` again on the summarized data.

@@

dim(year_sim_summ)

# check continuous
check_continuous(data = year_sim_summ,
                 dates = date)

# we can demonstrate an error by removing the Oct 8 (100th day)
check_continuous(data = year_sim_summ[-100,],
                 dates = date)

# it is useful to plot again to check your summarized data
plot_check_temp(data = year_sim_summ,
                dates = date,
                temperature = daily_temp,
                temp_min = 0, # temp_min and max lines are 
                              # user customizable
                temp_max = 15)
```

>>>>

```{r}
plot_check_temp(data = year_sim,
                dates = date,
                temperature = temp,
                temp_min = 0, # temp_min and max lines are 
                              # user customizable
                temp_max = 25)
```

There are no obvious outliers but since each day has 48 records, we need to summarize it to daily mean temperature with `summarize_temp()` and then check for missing days with `check_continuous()`. We also recommend using `plot_check_temp()` again on the summarized data (though leave out the resulting plot for space efficiency in this manuscript).

@@

# now a year's worth of single-day data
dim(year_sim_summ)

# check continuous (no errors)
check_continuous(data = year_sim_summ,
                 dates = date)

# we can demonstrate an error by removing Oct. 8 (100th day)
check_continuous(data = year_sim_summ[-100,],
                 dates = date)

```{r, eval=FALSE}
# it is useful to plot again to check your summarized data
plot_check_temp(data = year_sim_summ,
                dates = date,
                temperature = daily_temp,
                temp_min = 0, # temp_min and max lines are 
                              # user customizable
                temp_max = 15)
```
